Landscape heterogeneity simulation figures

### 2018-05-18 Manuscript_figures_2017_12_12.Rmd
Added code for Fig. S9

##Figure 1
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

@@

##Figure 1- vertical
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

@@

#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
A<-ggplot(imp_logit, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     ylab("Mean Decrease in Accuracy (%IncMSE)") +
    #ylab("")+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title=element_text(size=6)) 
    #theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))
    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
A

#imp_logitprev$SD<-rep(0.0000001, times=nrow(imp_logitprev))
B<-ggplot(imp_logitprev, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab(NULL)+
    theme_bw()+ theme(plot.margin = unit(c(0.25, 0, 0, 0), "cm"))+
    #ggtitle("(B)") + #" Variable Importance for Maximum \nPrevalence|Success") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8))
    #theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))
    #coord_flip()
B

#imp_logitdur$SD<-rep(100, times=nrow(imp_logitdur))
C<-ggplot(imp_logitdur, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
    #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab(NULL)+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(C)") + #" Variable Importance for Epidemic \nDuration|Success") +

@@

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

@@

##Figure 2
Box plots rec rate vs. density
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
colnames(sub_data)[3]<-"d" #rename density as "d"
colnames(sub_data)[11]<-"r" #rename perceptual range as "r"
#means <- aggregate(max_prevalence ~ density+ rec_rate +percep, sub_data, mean)
#means_dur <- aggregate(duration ~ density+ rec_rate +percep, sub_data, mean)

@@

##Figure 3
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=max_prevalence,fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=6))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

@@

##Figure 4
Comparing effects on landscape structure for select RSFs holding density, recovery rate and perceptual range constant.
```{r}
#sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data<-merged_data

@@

##Supplementary Figure S1
Box plot of percep vs. rec rate vs. density for every RSF combination
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data25<-sub_data[which(sub_data$density==0.25),]
sub_data50<-sub_data[which(sub_data$density==0.5),]

@@

##Supplementary Figure S2 (Heat maps, density=0.25)
Heatmap of max prevelance and mean duration for conspecific density=0.25 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.25),]

@@

##Supplementary Figure S3 (Heat maps, density=0.5)
Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]

@@

##Figure S4
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

@@

##Fig. S5
Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
```{r}
#sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data<-merged_data

@@

##Supplementary Figure S6
See SimpleSIR.Rmd

@@

##Figure S8
Representation of neutral landscapes used for simulation studies
```{r}
#' Create neutral landscape maps
library(raster)

@@

>>>>

## Figure 1
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

@@

## Figure 1- vertical
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

@@

#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
A<-ggplot(imp_logit, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     ylab("Mean Decrease in Accuracy (%IncMSE)") +
    #ylab("")+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title=element_text(size=6)) 
    #theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))
    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
A

#imp_logitprev$SD<-rep(0.0000001, times=nrow(imp_logitprev))
B<-ggplot(imp_logitprev, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab(NULL)+
    theme_bw()+ theme(plot.margin = unit(c(0.25, 0, 0, 0), "cm"))+
    #ggtitle("(B)") + #" Variable Importance for Maximum \nPrevalence|Success") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8))
    #theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))
    #coord_flip()
B

#imp_logitdur$SD<-rep(100, times=nrow(imp_logitdur))
C<-ggplot(imp_logitdur, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
    #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab(NULL)+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(C)") + #" Variable Importance for Epidemic \nDuration|Success") +

@@

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

@@

## Figure 2
Box plots rec rate vs. density
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
colnames(sub_data)[3]<-"d" #rename density as "d"
colnames(sub_data)[11]<-"r" #rename perceptual range as "r"
#means <- aggregate(max_prevalence ~ density+ rec_rate +percep, sub_data, mean)
#means_dur <- aggregate(duration ~ density+ rec_rate +percep, sub_data, mean)

@@

## Figure 3
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=max_prevalence,fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=6))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

@@

## Figure 4
Comparing effects on landscape structure for select RSFs holding density, recovery rate and perceptual range constant.
```{r}
#sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data<-merged_data

@@

## Supplementary Figure S1
Box plot of percep vs. rec rate vs. density for every RSF combination
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data25<-sub_data[which(sub_data$density==0.25),]
sub_data50<-sub_data[which(sub_data$density==0.5),]

@@

## Supplementary Figure S2 (Heat maps, density=0.25)
Heatmap of max prevelance and mean duration for conspecific density=0.25 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.25),]

@@

## Supplementary Figure S3 (Heat maps, density=0.5)
Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]

@@

## Figure S4
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

@@

## Fig. S5
Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
```{r}
#sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data<-merged_data

@@

## Supplementary Figure S6
See SimpleSIR.Rmd

@@

## Figure S8
Representation of neutral landscapes used for simulation studies
```{r}
#' Create neutral landscape maps
library(raster)

@@

## Figure S9
Random forest variable importance results from `party` package using cforest function
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Party Package May 2018")

#Load importance values (not scaled by SD)
imp_logit<-read.csv("partyRF_logit1000.csv")
imp_logitprev<-read.csv("partyRF_logitprev1000.csv")
imp_logitdur<-read.csv("partyRF_logitdur1000.csv")

#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
A<-ggplot(imp_logit, aes(x=reorder(X, x), y=x)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     ylab("Mean Decrease in Accuracy") +
    #ylab("")+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title=element_text(size=6)) 
    #theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))
    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
A

#imp_logitprev$SD<-rep(0.0000001, times=nrow(imp_logitprev))
B<-ggplot(imp_logitprev, aes(x=reorder(X, x), y=x)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     #ylab("Mean Decrease in Accuracy") +
    ylab(NULL)+
    theme_bw()+ theme(plot.margin = unit(c(0.25, 0, 0, 0), "cm"))+
    #ggtitle("(B)") + #" Variable Importance for Maximum \nPrevalence|Success") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8))
    #theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))
    #coord_flip()
B

#imp_logitdur$SD<-rep(100, times=nrow(imp_logitdur))
C<-ggplot(imp_logitdur, aes(x=reorder(X, x), y=x)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
    #ylab("Mean Decrease in Accuracy") +
    ylab(NULL)+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(C)") + #" Variable Importance for Epidemic \nDuration|Success") +

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
tiff("FigureS9_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()
